Turbulence in compact to giant HII regions

### 2022-03-11 strucfunc_paper.tex
Minor edit

\subsubsection{Hubble X and Hubble V in NGC 6822}
\label{sec:6822-hubble}
%Note to me: incomplete section. Find more regions info and finish asap.
The irregular dwarf galaxy, NGC 6822, is located at a distance of 500 kpc \citetext{\SI{1}{\arcsecond} = \SI{2.42}{pc} ; \citealp{2012A&A...540A.135S}} and the brightest HII regions are Hubble X and Hubble V (HX and HV hereafter). %(1'' = 2.4 pc)
%HV has a characteristic length of 100 pc and HX has a characteristic length of 140 pc \citep{1999PASP..111.1382O}.
Luminosity \ha{} for HV is \SI{e38.3}{erg.s^{-1}} and for HX is \SI{e38.21}{erg.s^{-1}} \citep{2002MNRAS.329..481B}.
Two recognized OB associations are identified within these HII regions \citep{1991ApJ...379..621H,1992AJ....104.1374W}.
HV is located near 'Hodge OB 8' and HX is located near 'Hodge OB13'  \citep{1999PASP..111.1382O}.

@@

Figure~\ref{fig:velocity-maps} shows maps of the \ha{} centroid velocity
\(V_c\) for each \hii{} region in our sample,
calculated as described above in section~\ref{sec:spectr-datas}
and after subtracting the mean systemic velocity,
\(\left\langle V_c\right\rangle\) in each case.
% The color scheme ranges from the most negative velocities in blue
% to the most positive velocities in red,
% but the amplitude of the velocity fluctuations differs considerably between regions,
% as indicated by the color scale bar on each map,
% ranging from \SI{\pm 7}{km.s^{-1}} for the Lagoon
% up to  \SI{\pm 40}{km.s^{-1}} for 30~Doradus.
The overall amplitude of the plane-of-sky
velocity fluctuations can be characterized by a dispersion,
\(\sigma\pos\), defined as:
\begin{equation}
  \label{eq:sig-pos}
  \sigma^2\pos =
  \left\langle 
  \bigl[ V_c (\xx_i) -\langle V_ c\rangle  \bigr]^2
  \right \rangle ,
\end{equation}
where the average is performed over all observed points \(i\)
in a given map.
Note that \(\sigma\pos\) is also the RMS width of
the probability density function (PDF) of \(V_c\).
This PDF for each region is shown in Figure~\ref{fig:hist}
on a common velocity scale and arranged in order of decreasing \(\sigma\pos\).
It can be seen that the amplitude of the
velocity fluctuations varies considerably between regions,
with \(\sigma\pos\) in 30~Dor being more than 5 times higher than in 
nearby regions such as Orion.

@@

\begin{figure*}
 \centering
 \includegraphics[width=5in]{Figures/Hist}\par
 \caption{
   Histograms of the plane-of-sky variation in the \ha{} centroid velocities.
   Each panel shows the fraction of the observed spatial points
   (pixels or fiber positions)
   with a given velocity offset from the mean systemic velocity of each region.
   The RMS width \(\sigma\pos\) of each distribution is marked,
   as is the number of spatial points.
   The bin width is \SI{1}{km.s^{-1}} and the regions are arranged
   in order of decreasing \(\sigma\pos\).
 }
 \label{fig:hist}
\end{figure*}

\subsection{The second-order structure function}
\label{sec:second-order-struct}
% One of the fundamental properties of turbulent clouds must be spatial fluctuations in velocity and density.                                     
% These fluctuations are observed as projected spatial fluctuations in the average line-of-sight velocity and integrated column density.
% It is possible to describe the statistical properties of these fluctuations if they are assumed as a product of a stochastic field \citep{1984ApJ...277..556S}. 
% This previous assumption give us the ability to apply statistical tools to the velocity field and the analysis of the velocity pattern is reduced to the calculation of the averages and correlations.

@@

Two observational effects can modify the observed structure function at the smallest scales.
The first is the blurring of the observed image by atmospheric seeing,
which tends to reduce \(B(r)\) for small \(r\).
In Appendix~\ref{sec:effects-seeing-struc}, we perform numerical experiments
with synthetic velocity fields and find that
a good approximation to the effects of seeing is to multiply
the model structure function by a factor:
\begin{equation}\label{eq:ffs}
   S(r; s_0, r_0) = \frac{
    e^{-s_0 / r_0}
  }{
    1+(2s_0 / r)^{2 / 3}
  } ,
\end{equation}
where \(s_0\) is the RMS width of the seeing profile.\footnote{%
  Note that the full-width half maximum (FWHM) seeing width is
  \(2 (2 \ln 2)^{1/2} s_0 \approx 2.35 s\).
}
An example is shown by the green line in Figure~\ref{fig:model-strucfunc}a.
Note that the effect of seeing is to make the structure function 
bend down away from the idealized power law, 
becoming increasingly steep at scales smaller than \(s_0\),
but having a noticeable effect at scales up to \(10 s_0\).

@@

Combining both the effects of seeing and noise yields the corrected
model structure function:
\begin{multline}
  \tilde{B}
  \bigl( r; \ r_0, \sigma^2\pos, m, s_0, B_{\text{noise}} \bigr)
  = \\
  2\sigma^2\pos \left[
    1 - 2^{- \left( r/r_0 \right)^m} 
  \right]
  \,  S(r; s_0, r_0) + B_{\text{noise}}
\label{eq:sf-corrected}
\end{multline}

An example model structure function that is affected by both seeing and noise

@@

Considering the previous models we obtain the final form of our proposed structure function functional:
%
\begin{equation}\label{eq:sf-functional}
B_{\text{func}}(r) = B(r; \beta r_0, \beta \sigma^2,m) \times S(r; s_0, r_0) + B_{\text{noise}}
\end{equation}
%
where the term \( B_{\text{noise}}\) is a correction factor that considers the instrument noise at small scales.
This noise would have the effect of flattening the structure function by removing the effects of the fluctuations which would be interpreted as an uncorrelated field.

The results obtained with equation \ref{eq:Br} are use in a non-linear least-squares fit with the equation \ref{eq:sf-functional} used as an objective function.
For this purpose we use the \textit{python} package \textit{lmfit} \citep{newville_matthew_2014_11813} where the equation \ref{eq:Br} and \ref{eq:sf-functional} are use in a chi-square statistic defined as:
%
%\begin{equation}\label{eq:chi}
%  \chi^2 = \sum_i ^N \frac{[y_i^{\text{measure}}-y_i^{\text{model}} (\boldsymbol{v})]^2}{\epsilon_i ^2}
%\end{equation}
%
%
\begin{equation}\label{eq:chi}
  \chi^2 = \sum_i ^N \frac{[B(r)-B_{\text{func}}(r;r_0, \sigma^2\pos, m, s_0, B_{\text{noise}})]^2}{\varepsilon_i ^2}
\end{equation}
%
where the turbulent parameters are \(r_{0}\)\ , \(\sigma^2\pos\) and \(m\), and the observational constraints \(s_0\) and \( B_{\text{noise}}\).
This procedure calculate a value \(\chi\) to be minimized scaled by the inverse of the uncertainty \(\varepsilon\) in the data.
To obtain the confidence intervals we use the minimization procedure \textit{emcee} \citep{2013PASP..125..306F} which is a \textit{python} implementation of the affine-invariant ensemble sampler for Markov chain Monte Carlo (MCMC) by \citet{2010CAMCS...5...65G}.  
%Using these procedure we obtain the posteriors for our model and the parameters in equation~\ref{eq:chi}.

%In this way we want to avoid one fundamental problem in the interpretation of the structure function. 
%The slope in the majority of previous studies and hence, the correlation length, is obtained without a formal procedure. 
%The traditional way to find the correlation length it is to determine a particular range of ascending values in the structure function. 
%If this increase in values is stopped or reversed it is commonly assumed that one particular inertial range has been found. 
%In some cases this procedure keeps going up to large scales, giving two or more inertial regimes leading to an erroneous interpretation of multiple inertial scales.

@@

@@

In this section we present and describe the second-order structure results. The structure functions are plotted against separation in parsecs and we also show the posteriors of the turbulent parameters using the analysis discussed in section~\ref{sec:methods-apply}.

\subsection{HII regions second-order structure functions and turbulent parameters}

%structure functions plots descriptions
Figures \ref{fig:strucfunc-fit-OrionS}-\ref{fig:strucfunc-fit-OrionLH} left panels show in solid and open blue circles the observational structure function that we compute using equation \ref{eq:Br} on the \ha{} velocity fields of Fig. \ref{fig:velocity-maps}. 
In the plots the solid circles indicate the points we use in the non-linear regression analysis (see section~\ref{sec:methods-apply}), while the open circles are the points of the structure function that where left out.
The criteria for the previous considerations is that the structure function at large separations is affected by the inhomogeneties of the velocity field (see section-\ref{sec:limit-model-struct}), hence the reason that large separation values are not considered for the fit of our model. 
In some cases, at the smallest separations we merge a couple of the structure functions points under the assumption that those would be heavily affected by the seeing and the rest would be coincident with the power-law behavior.
The Figures shows in the orange solid thick line the best fit for the equation \ref{eq:sf-functional} which takes into account observational limitations on the structure function.
The green dashed line indicate the theoretical model for the structure function using equation \ref{eq:functional}.

Figures \ref{fig:strucfunc-fit-OrionS}-\ref{fig:strucfunc-fit-OrionLH} left panels show in dashed and dotted lines the parameters of our model.
The vertical dashed line indicates the correlation length, \(r_0\), and the horizontal dashed line indicates the true variance of the velocity fields, \(\sigma^2\).
The vertical and horizontal dotted lines shows the value of the observational considerations: the rms seeing, \(s_0\) and the value of the noise, \(B_{\text{noise}}\).
For the dashed and dotted lines the overlapping translucent boxes indicate the confidence intervals in 1-sigma (dark shaded area) and 2-sigma (light shaded area) obtained from the MCMC analysis.
The light shaded areas in the plot show where the separation \(r\) is above half of the box size, \(L\), which is indicated with a vertical dotted line.
To present our results in the next paragraphs the small scales would refer to the separations \(r < r_0\) and large scales would refer to separations \(r > r_0\).

Figure~\ref{fig:strucfunc-fit-OrionS}a shows the structure function of the Orion core.
Valid scales are consider above the separation of \SI{0.002}{pc} (\(s_0\)=\SI{1}{\arcsecond}).
In this case we merge the first three points.
From there until separations of \SI{0.003}{pc} all points within this range fall below the true model showing that they are affected by the seeing. 
The correlation length for the Orion core is \SI{0.07 \pm 0.01}{pc}, it has a \(\sigma^2\pos\) of \SI{12 \pm 1}{km^{2}.s^{-2}} and an index of \num{1.07 \pm 0.02}.
The structure function of the Orion core behaves accordingly to the tapered case of inhomogeneous fluctuations (see Figure~\ref{fig:model-strucfunc}b).
At large scales there is a plateau around \SI{22}{km^{2}.s^{-2}} reached at \SI{0.25}{pc}.
Above separations of \SI{0.3}{pc} the structure function decays reaching a separation of \SI{0.5}{pc} with a value of \SI{7}{km^{2}.s^{-2}}.

The Figure~\ref{fig:strucfunc-fit-M8}a shows the structure function of the Lagoon nebula.
There aren't any points affected by the seeing which has a value of \SI{0.006}{pc} (\(s_0\)=\SI{1}{\arcsecond}).
In this case we merge the first two points.
The Lagoon nebula presents a non-uniform behavior below the correlation length but it is possible to see the characteristic ascending values of the structure function.
The turbulent parameters that fits our model are a \(r_0\) of \SI{1 \pm 0.2}{pc}, a \(\sigma^2\pos\) of \SI{7 \pm 1}{km^{2}.s^{-2}} and an index of \num{1.13 \pm 0.01}.
At large scales there is an indication of some periodic behavior with a very large amplitude of ascending \(B(r)\) at largest separation.
The first maximum value of \(B(r)\) in the order of 2\(\sigma^2\pos\) is \(\sim\)\SI{14}{km^{2}.s^{-2}} at a separation of \(\sim\)\SI{2.5}{pc}. 
Considering an oscillating behavior at \SI{4.5}{pc} a minimum value of \SI{11}{km^{2}.s^{-2}} is reached.
From this point the structure function keeps going up until it reaches \SI{66}{km^{2}.s^{-2}} around \SI{20}{pc}.

The Figure~\ref{fig:strucfunc-fit-CarC}a shows the structure function of the Carina nebula.
The seeing is \SI{0.008}{pc} (\(s_0\)=\SI{1.3}{\arcsecond}) and there are just a couple of points that lie below the true model, indicating that the majority of points isn't affected by the seeing.
For this region we merge the first two points of the structure function.
As the Lagoon nebula, Carina also shows a non-uniform behavior below the correlation length.
The correlation length is \SI{0.56 \pm 0.04}{pc} pc at a \(\sigma^2\pos\) of \SI{18 \pm 1}{km^{2}.s^{-2}}  and an index of \num{1.14 \pm 0.01}.
At larges scales the structure function of the Carina nebula follows a pattern that closely resembles the homogeneous fluctuation of Figure~\ref{fig:model-strucfunc}a.
The structure function reaches a plateau around \SI{36}{km^{2}.s^{-2}} at \(\sim\) \SI{2}{pc}.
When \(r >\)\SI{6}{pc} the structure functions resembles a periodic behavior with a small amplitude.

For Carina and Lagoon nebula, the velocity fields are obtained from the FLAMES multi-fiber instrument (section~\ref{sec:flames-multi-fiber}). 
We can see from Figure~\ref{fig:velocity-maps} that observations from this instrument do not give uniform maps as the other instruments. 
Instead the discrete fiber positions are diversely located across the FOV.
This would affect the structure function since the values are not adjacent as the other observations.
This is reflected in the non uniform \(B(r)\) below  \(r_0\) that we pointed out in the previous paragraphs.

The Figure~\ref{fig:strucfunc-fit-N346}a shows the structure function of NGC 346.
In this case we merge the first three points of the structure function.
For this region the points are above the seeing value which is \SI{0.07}{pc} (\(s_0\)=\SI{0.23}{\arcsecond}) and the first ten points lie below the true model.
At separations above \SI{0.4}{pc} the observed structure functions is coincident with the true model. 
The correlation length is \SI{2 \pm 0.1}{pc} at a \(\sigma^2\pos\) of \SI{3 \pm 1}{km^{2}.s^{-2}} and an index of \num{0.76 \pm 0.02}.
For scales above \SI{9}{pc} with a \(B(r)\) value of \SI{70}{km^{2}.s^{-2}} a periodic behavior is seen .
Starting from a separation of \SI{12}{pc} and a \(B(r)\) value of \SI{65}{km^{2}.s^{-2}} the structure function keeps ascending until it reaches \SI{146}{km^{2}.s^{-2}} at \SI{24}{pc}.

The 30 Doradus structure function is shown in Figure~\ref{fig:strucfunc-fit-Dor}a.
In this case we merge the first five points of the structure function.
The seeing value for this regions is \SI{0.16}{pc} (\(s_0\)=\SI{0.7}{\arcsecond}) and just one point of the structure function is below this value.
Until a separation of \SI{1.7}{pc} the structure function lies below the true model.
The correlation length is \SI{4 \pm 0.2}{pc} at a \(\sigma^2\pos\) of \SI{300 \pm 9}{km^{2}.s^{-2}} and an index of \num{0.84 \pm 0.04}.
30 Doradus structure function presents a behavior of tapered fluctuations.  
The maximum \(B(r)\) value is \SI{655}{km^{2}.s^{-2}} at a separation of \SI{21}{pc}. 
From there \(B(r)\) values descends until they reach \SI{250}{km^{2}.s^{-2}} at \SI{38}{pc}.

In the Figure~\ref{fig:strucfunc-fit-HV}a we show the structure function of Hubble V.
For the observations coming from the TAURUS-II instrument there wasn't any merging of points.
The value of the seeing for this regions is \SI{0.5}{pc} (\(s_0\)=\SI{0.2}{\arcsecond}).
All the structure function points lies below the true model which would indicate that the seeing is affecting the observed structure function.
The correlation length is \SI{3.4 \pm 0.3}{pc} at a \(\sigma^2\pos\) of  \SI{10 \pm 1}{km^{2}.s^{-2}} and an index of \num{0.74 \pm 0.10}.
The maximum \(B(r)\) value is \SI{18}{km^{2}.s^{-2}} at a separation of \SI{25}{pc}. 
From there \(B(r)\) values descends until \SI{14}{km^{2}.s^{-2}} at \SI{45}{pc}, then it rises for the next point at \SI{50}{pc} with a value of \SI{15}{km^{2}.s^{-2}} and finally the structure functions descends at \SI{9}{km^{2}.s^{-2}} for a separation of \SI{70}{pc}.

The Hubble X structure function is shown in Figure~\ref{fig:strucfunc-fit-HX}a.
The seeing is \SI{0.006}{pc} (\(s_0\)=\SI{0.24}{\arcsecond}) and as in Hubble V the observed structure function lies below the true model.
The correlation length is \SI{4 \pm 0.4}{pc} at a \(\sigma^2\pos\) of \SI{16 \pm 1}{km^{2}.s^{-2}} and an index of \num{0.88 \pm 0.14}.
The structure functions presents at large scales the behavior of periodic fluctuations with a small amplitude.
A plateau is reached around \SI{25}{km^{2}.s^{-2}} at a separation of \SI{14}{pc} and a maximum \(B(r)\) value of \SI{31}{km^{2}.s^{-2}} at a separation of \SI{36}{pc}. 
From this point the structure functions shows consistent values around \SI{24}{km^{2}.s^{-2}} and finally there is a rise for the last point to \SI{29}{km^{2}.s^{-2}} at a separation of \SI{91}{pc}.

In the Figure~\ref{fig:strucfunc-fit-N595}a we show the structure function of NGC 595.
The seeing is \SI{0.5}{pc} (\(s_0\)=\SI{0.12}{\arcsecond}) and for this region only the first two points are below the true model. 
The correlation length is \SI{12 \pm 1}{pc} at a \(\sigma^2\pos\) of \SI{56 \pm 2}{km^{2}.s^{-2}} and an index of \num{1.3 \pm 0.05}.
At large scales the structure function behave following the tapered fluctuations behavior.
A maximum \(B(r)\) value of \SI{104}{km^{2}.s^{-2}} is reached at \SI{33}{pc}. 
From there the structure functions decays following and inhomogeneous pattern until it reaches \SI{54}{km^{2}.s^{-2}} at a separation of \SI{211}{pc}.

>>>>

\subsubsection{Hubble X and Hubble V in NGC 6822}
\label{sec:6822-hubble}
%Note to me: incomplete section. Find more regions info and finish asap.
The irregular dwarf galaxy, NGC 6822, is located at a distance of 500 kpc \citetext{\SI{1}{\arcsecond} = \SI{2.42}{pc} ; \citealp{2012A&A...540A.135S}} and the brightest HII regions are Hubble X and Hubble V (HX and HV hereafter). %(1'' = 2.4 pc)
%HV has a characteristic length of 100 pc and HX has a characteristic length of 140 pc \citep{1999PASP..111.1382O}.
Luminosity \ha{} for HV is \SI{e38.3}{erg.s^{-1}} and for HX is \SI{e38.21}{erg.s^{-1}} \citep{2002MNRAS.329..481B}.
Two recognized OB associations are identified within these HII regions \citep{1991ApJ...379..621H,1992AJ....104.1374W}.
HV is located near 'Hodge OB 8' and HX is located near 'Hodge OB13'  \citep{1999PASP..111.1382O}.
\citet{1993PASJ...45..693T} realize a study on the kinematics of HX and HV.

@@

Figure~\ref{fig:velocity-maps} shows maps of the \ha{} centroid velocity
\(V_c\) for each \hii{} region in our sample,
calculated as described above in section~\ref{sec:spectr-datas}
and after subtracting the mean systemic velocity,
\(\left\langle V_c\right\rangle\) in each case.
% The color scheme ranges from the most negative velocities in blue
% to the most positive velocities in red,
% but the amplitude of the velocity fluctuations differs considerably between regions,
% as indicated by the color scale bar on each map,
% ranging from \SI{\pm 7}{km.s^{-1}} for the Lagoon
% up to  \SI{\pm 40}{km.s^{-1}} for 30~Doradus.
The overall amplitude of the plane-of-sky
velocity fluctuations can be characterized by a dispersion,
\(\sigma\pos\), defined as:
\begin{equation}
  \label{eq:sig-pos}
  \sigma^2\pos =
  \left\langle 
  \bigl[ V_c (\xx_i) -\langle V_ c\rangle  \bigr]^2
  \right \rangle ,
\end{equation}
where the average is performed over all observed points \(i\)
in a given map.
Note that \(\sigma\pos\) is also the RMS width of
the probability density function (PDF) of \(V_c\).
This PDF for each region is shown in Figure~\ref{fig:pdfs}
on a common velocity scale and arranged in order of decreasing \(\sigma\pos\).
It can be seen that the amplitude of the
velocity fluctuations varies considerably between regions,
with \(\sigma\pos\) in 30~Dor being more than 5 times higher than in 
nearby regions such as Orion.

@@

\begin{figure*}
 \centering
 \includegraphics[width=5in]{Figures/pdfs}\par
 \caption{
   Histograms of the plane-of-sky variation in the \ha{} centroid velocities.
   Each panel shows the fraction of the observed spatial points
   (pixels or fiber positions)
   with a given velocity offset from the mean systemic velocity of each region.
   The RMS width \(\sigma\pos\) of each distribution is marked,
   as is the number of spatial points.
   The bin width is \SI{1}{km.s^{-1}} and the regions are arranged
   in order of decreasing \(\sigma\pos\).
 }
 \label{fig:pdfs}
\end{figure*}

\subsection{The second-order structure function}
\label{sec:second-order-struct}

@@

Two observational effects can modify the observed structure function at the smallest scales.
The first is the blurring of the observed image by atmospheric seeing,
which tends to reduce \(B(r)\) for small \(r\).
In Appendix~\ref{sec:effects-seeing-struc}, we perform numerical experiments
with synthetic velocity fields and find that
a good approximation to the effects of seeing is to multiply
the model structure function by a factor:
\begin{equation}\label{eq:ffs}
   S(r; s_0, r_0) = \frac{
    e^{-s_0 / r_0}
  }{
    1+(2s_0 / r)^{2 / 3}
  } ,
\end{equation}
where \(s_0\) is the RMS width of the seeing profile.\footnote{%
  Note that the full-width half maximum (FWHM) seeing width is
  \(2 (2 \ln 2)^{1/2} s_0 \approx 2.35 s_0\).
}
An example is shown by the green line in Figure~\ref{fig:model-strucfunc}a.
Note that the effect of seeing is to make the structure function 
bend down away from the idealized power law, 
becoming increasingly steep at scales smaller than \(s_0\),
but having a noticeable effect at scales up to \(10 s_0\).

@@

Combining both the effects of seeing and noise yields the corrected
model structure function:
\begin{multline}
  \tilde{B}
  \bigl( r; \ r_0, \sigma^2\pos, m, s_0, B_{\text{noise}} \bigr)
  = \\
  2\sigma^2\pos \left[
    1 - 2^{- \left( r/r_0 \right)^m} 
  \right]
  \,  S(r; s_0, r_0) + B_{\text{noise}}
\label{eq:sf-functional}
\end{multline}
An example of this equation is shown by the red line in Figure~\ref{fig:model-strucfunc}.

@@

%\begin{equation}\label{eq:sf-functional}
%B_{\text{func}}(r) = B(r; \beta r_0, \beta \sigma^2,m) \times S(r; s_0, r_0) + B_{\text{noise}}
%\end{equation}

@@

\subsubsection{Model fitting and estimation of confidence intervals}
\label{sec:model-fit}

The results obtained with equation \ref{eq:Br} are use in a non-linear least-squares fit with the equation \ref{eq:sf-functional} used as an objective function.
For this purpose we use the \textit{python} package \textit{lmfit} \citep{newville_matthew_2014_11813} which implement a chi-square statistic defined as:
%
%\begin{equation}\label{eq:chi}
%  \chi^2 = \sum_i ^N \frac{[y_i^{\text{measure}}-y_i^{\text{model}} (\boldsymbol{v})]^2}{\epsilon_i ^2}
%\end{equation}
%
%
\begin{equation}\label{eq:chi}
  \chi^2 = \sum_i ^N \frac{[B(r)-B_{\text{func}}(r;r_0, \sigma^2\pos, m, s_0, B_{\text{noise}})]^2}{\varepsilon_i ^2}
\end{equation}
%
where the turbulent parameters, \(r_{0}\)\, \(\sigma^2\pos\) and \(m\), and the observational constraints \(s_0\) and \( B_{\text{noise}}\), are the set of variables to be optimized in the fit.
This procedure calculate a value \(\chi\) to be minimized scaled by the inverse of the uncertainty \(\varepsilon\) in the data using the Levenberg-Marquardt (LM) method.
Then we proceed to obtain the confidence intervals using the minimization procedure \textit{emcee} \citep{2013PASP..125..306F} which is a implementation of the affine-invariant ensemble sampler for Markov chain Monte Carlo (MCMC) by \citet{2010CAMCS...5...65G}.

@@

In this section we present and describe the second-order structure results. The structure functions are plotted against separation in parsecs and we also show the posteriors of the parameters discussed in the previous section.

\subsection{HII regions second-order structure functions}

%structure functions plots descriptions
Figures \ref{fig:strucfunc-fit-OrionS}-\ref{fig:strucfunc-fit-OrionLH} left panels show in solid and open blue circles the observational structure function that we compute using equation \ref{eq:Br} on the \ha{} velocity fields of Fig. \ref{fig:velocity-maps}. 
In the plots the solid circles indicate the points we use in the non-linear regression analysis (see section~\ref{sec:model-fit}), while the open circles are the points of the structure function that where left out.
The criteria for the previous considerations is that the structure function at large separations is affected by the inhomogeneties of the velocity field (see section-\ref{sec:limit-model-struct}), hence the reason that large separation values are not used since they are not consider in our model. 
In some cases, at the smallest separations we merge a couple of the structure functions points under the assumption that those would be heavily affected by the seeing and the rest would be coincident with the power-law behavior.
The Figures shows in the orange solid thick line the best fit for the equation \ref{eq:sf-functional} which takes into account observational limitations on the structure function.
The green dashed line indicate the theoretical model for the structure function using equation \ref{eq:functional}.

Figures \ref{fig:strucfunc-fit-OrionS}-\ref{fig:strucfunc-fit-OrionLH} left panels show in dashed and dotted lines the parameters of our model.
The vertical dashed line indicates the correlation length, \(r_0\), and the horizontal dashed line indicates the true variance of the velocity fields, \(\sigma^2\).
The vertical and horizontal dotted lines shows the value of the observational considerations: the rms seeing, \(s_0\) and the noise, \(B_{\text{noise}}\).
These values were obtained using the LM method.
For the dashed and dotted lines the overlapping translucent boxes indicate the confidence intervals in 1-sigma (dark shaded area) and 2-sigma (light shaded area) obtained from the MCMC analysis.
The light shaded areas in the plot show where the separation \(r\) is above half of the box size, \(L\), which is indicated with a vertical dotted line.
%For the discussion of our results in the next paragraphs the small scales would refer to the separations \(r < r_0\) and large scales would refer to separations \(r > r_0\).

Figure~\ref{fig:strucfunc-fit-OrionS}a shows the structure function of the Orion core.
Valid scales are consider above the separation of \SI{0.002}{pc} (\(s_0\)=\SI{1}{\arcsecond}).
In this case we merge the first three points of the structure function.
From \SI{0.002}{pc} until \SI{0.003}{pc} all points fall below the true model showing that they are affected by the seeing. 
The correlation length for the Orion core is \SI{0.07}{pc}, it has a \(\sigma^2\pos\) of \SI{12}{km^{2}.s^{-2}} and an index of \num{1.07}.
The structure function of the Orion core behaves accordingly to the tapered case of inhomogeneous fluctuations (see Figure~\ref{fig:model-strucfunc}b).
At \SI{0.25}{pc} there is a plateau around \SI{22}{km^{2}.s^{-2}}.
Above separations of \SI{0.3}{pc} the structure function decays to a value of \SI{7}{km^{2}.s^{-2}} at  \SI{0.5}{pc}.

The Figure~\ref{fig:strucfunc-fit-M8}a shows the structure function of the Lagoon nebula.
There aren't any points affected by the seeing which has a value of \SI{0.006}{pc} (\(s_0\)=\SI{1}{\arcsecond}).
In this case we merge the first two points.
The Lagoon nebula presents a non-uniform behavior below the correlation length but it is possible to see the characteristic ascending values of the structure function.
The turbulent parameters that fits our model are a \(r_0\) of \SI{1}{pc}, a \(\sigma^2\pos\) of \SI{7}{km^{2}.s^{-2}} and an index of \num{1.17}.
At large scales there is an indication of some periodic behavior followed by ascending \(B(r)\) values at largest separation.
The first maximum value of \(B(r)\) in the order of 2\(\sigma^2\pos\) is \(\sim\)\SI{14}{km^{2}.s^{-2}} at a separation of \(\sim\)\SI{2.5}{pc}. 
Considering an oscillating behavior at \SI{4.5}{pc} a minimum value of \SI{11}{km^{2}.s^{-2}} is reached.
From this point the structure function ascends until it reaches \SI{66}{km^{2}.s^{-2}} around \SI{20}{pc}.

The Figure~\ref{fig:strucfunc-fit-CarC}a shows the structure function of the Carina nebula.
The seeing is \SI{0.008}{pc} (\(s_0\)=\SI{1.3}{\arcsecond}) and there are just a couple of points that lie below the true model, indicating that the majority of points isn't affected by the seeing.
For this region we merge the first two points of the structure function.
As the Lagoon nebula, Carina also shows a non-uniform behavior below the correlation length.
The correlation length is \SI{0.56}{pc} pc at a \(\sigma^2\pos\) of \SI{18}{km^{2}.s^{-2}} and an index of \num{1.14}.
At larges scales the structure function of the Carina nebula follows a pattern that resembles the homogeneous fluctuation of Figure~\ref{fig:model-strucfunc}a.
The structure function reaches a plateau around \SI{36}{km^{2}.s^{-2}} at \(\sim\) \SI{2}{pc}.
When \(r >\)\SI{6}{pc} the structure functions shows a small amplitude periodic pattern around 2\(\sigma^2\pos\).

For Carina and Lagoon nebula, the velocity fields are obtained from the FLAMES multi-fiber instrument (section~\ref{sec:flames-multi-fiber}). 
We can see from Figure~\ref{fig:velocity-maps} that observations from this instrument do not give uniform maps as the others. 
Instead, the discrete fiber positions are diversely located across the FOV.
This would affect the structure function since the values are not adjacent as the other observations.
This is reflected in the non uniform \(B(r)\) below  \(r_0\) that we pointed out in the previous paragraphs.

The Figure~\ref{fig:strucfunc-fit-N346}a shows the structure function of NGC 346.
In this case we merge the first three points of the structure function.
The seeing value is \SI{0.07}{pc} (\(s_0\)=\SI{0.23}{\arcsecond}).
For this region the first ten points lie below the true model.
At separations above \SI{0.4}{pc} the observed structure functions is coincident with the true model. 
The correlation length is \SI{2}{pc} at a \(\sigma^2\pos\) of \SI{35}{km^{2}.s^{-2}} and an index of \num{0.80}.
For scales above \SI{12}{pc} and a \(B(r)\) value of \SI{65}{km^{2}.s^{-2}} the structure function shows a pattern of ascending values until it reaches \SI{146}{km^{2}.s^{-2}} at \SI{24}{pc}.

The 30 Doradus structure function is shown in Figure~\ref{fig:strucfunc-fit-Dor}a.
In this case we merge the first five points of the structure function.
The seeing value for this regions is \SI{0.16}{pc} (\(s_0\)=\SI{0.7}{\arcsecond}) and just one point of the structure function is below this value.
Until a separation of \SI{1.7}{pc} is reached, the structure function lies below the true model.
The correlation length is \SI{4}{pc} at a \(\sigma^2\pos\) of \SI{297 \pm 9}{km^{2}.s^{-2}} and an index of \num{0.85}.
At large separations 30 Doradus structure function presents a behavior of tapered fluctuations.  
The maximum \(B(r)\) value is \SI{655}{km^{2}.s^{-2}} at a separation of \SI{21}{pc}. 
From there \(B(r)\) values descends until they reach \SI{250}{km^{2}.s^{-2}} at \SI{38}{pc}.

In the Figure~\ref{fig:strucfunc-fit-HV}a we show the structure function of Hubble V.
For the observations coming from the TAURUS-II instrument there wasn't any merging of points at small scales.
The value of the seeing for this regions is \SI{0.5}{pc} (\(s_0\)=\SI{0.2}{\arcsecond}).
All the structure function points lies below the true model.
The correlation length is \SI{3.5}{pc} at a \(\sigma^2\pos\) of  \SI{10}{km^{2}.s^{-2}} and an index of \num{0.75}.
The maximum \(B(r)\) value is \SI{18}{km^{2}.s^{-2}} at a separation of \SI{25}{pc}. 
From there \(B(r)\) values descends until it reaches \SI{14}{km^{2}.s^{-2}} at \SI{45}{pc}, then it rises for the next point at \SI{50}{pc} with a value of \SI{15}{km^{2}.s^{-2}}.
Finally the structure functions descends at \SI{9}{km^{2}.s^{-2}} for a separation of \SI{70}{pc}.

The Hubble X structure function is shown in Figure~\ref{fig:strucfunc-fit-HX}a.
The seeing is \SI{0.6}{pc} (\(s_0\)=\SI{0.24}{\arcsecond}) and as in Hubble V the observed structure function lies below the true model.
The correlation length is \SI{4}{pc} at a \(\sigma^2\pos\) of \SI{15}{km^{2}.s^{-2}} and an index of \num{0.93}.
A plateau is reached around \SI{25}{km^{2}.s^{-2}} at a separation of \SI{14}{pc} and a maximum \(B(r)\) value of \SI{31}{km^{2}.s^{-2}} at a separation of \SI{36}{pc}.

In the Figure~\ref{fig:strucfunc-fit-N595}a we show the structure function of NGC 595.
The seeing is \SI{0.3}{pc} (\(s_0\)=\SI{0.1}{\arcsecond}) and for this region only the first two points are below the true model. 
The correlation length is \SI{12}{pc} at a \(\sigma^2\pos\) of \SI{54}{km^{2}.s^{-2}} and an index of \num{1.3}.
At large scales the structure function behaves following the tapered fluctuations pattern.
A maximum \(B(r)\) value of \SI{104}{km^{2}.s^{-2}} is reached at \SI{33}{pc}. 
From there the structure functions decays following and inhomogeneous pattern until it reaches \SI{54}{km^{2}.s^{-2}} at a separation of \SI{211}{pc}.

In the Figure~\ref{fig:strucfunc-fit-N604H}a we show the structure function of NGC 604.
The seeing is \SI{1.7}{pc} (\(s_0\)=\SI{0.42}{\arcsecond}) and the structure function of this region lies below the true model for most of the separation range.
The correlation length is \SI{10}{pc} at a \(\sigma^2\pos\) of \SI{71}{km^{2}.s^{-2}} and has an index of \num{1}.
The structure function present clear characteristics of periodic oscillations at large scales.
A periodic pattern for the structure function appears with a maximum \(B(r)\) value of \SI{143}{km^{2}.s^{-2}} that is reached at \SI{60}{pc}, then the oscillation cause a minimum of \SI{54}{km^{2}.s^{-2}} at \SI{133}{pc} and finally it goes back up again at \SI{211}{pc} to a \(B(r)\) value of \SI{123}{km^{2}.s^{-2}}.

The EON structure function is shown in Figure~\ref{fig:strucfunc-fit-OrionLH}a.
This observations are heavily affected by the noise which presents a value of \SI{6}{km^{2}.s^{-2}} which is larger that the \(\sigma^2\pos\) value of \SI{4}{km^{2}.s^{-2}}.
